THESIS PROJECT PROPOSAL

### 2019-11-16 project_ashish/paper.tex
Update paper.tex

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{./cd11.png}
	\caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
	\label{figure 1}
\end{figure}

@@

The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{ref:madgraph} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
A separate simulation of the detector is employed using \textsc{GEANT}~\cite{ref:geant} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width= 0.5 \columnwidth]{./sm.png}
	\caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
	\label{figure 1}
\end{figure}

@@

The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{alwall2014automated} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
A separate simulation of the detector is employed using \textsc{GEANT}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.
